Automated topic naming to support analysis of software maintenance activities

### 2010-08-18 icse/icse2011.tex
some todo notes and future work

\todo[inline]{Update this}

@@

\todo[inline]{More needs to be done here! More content!}

@@

% para 5 future work
% Future work
There are several avenues of further investigation.  
% Talk to people
We want to investigate developer attitudes related to these labels: i.e., when we label a topic, was the developer expressing positive or negative qualities about that label?  It is difficult to map abstract qualities to particular messages. 
% This is disjointed and needs more context
Is a ``quality'' discussion about more than just corrective maintenance? %In this study we take the position that any type of maintenance has to do with software quality.

\todo[inline]{Future work is disjointed the question should be more clear}

>>>>

\todo[inline]{Update this, rewrite it to handle the new situation but be sure to keep the maintainability and portability}

@@

\todo[inline]{More needs to be done here! More content!}
\todo[inline]{Use the old diagrams to come up with interesting comparisons}

@@

% para 5 future work
% Future work
There are several avenues of further investigation.  
% Talk to people
We want to investigate developer attitudes related to these labels: i.e., when we label a topic, was the developer expressing positive or negative qualities about that label?  It is difficult to map abstract qualities to particular messages. 
% This is disjointed and needs more context
On question we seek to answer is if a ``quality'' discussion about more than just corrective maintenance? %In this study we take the position that any type of maintenance has to do with software quality.

%\todo[inline]{Future work is disjointed the question should be more clear}
